---
title: "Deliverable Three"
author: "Nathaniel Jones"
output: word_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)
#install.packages("officedown")
#install.packages("officer")
#install.packages("magrittr")
#install.packages("tidyverse") 
#install.packages("ggpubr") 
#install.packages("gplots") 
#install.packages("ggfortify")
#install.packages("broom") 
#install.packages("multcompView") 
#install.packages('regclass')
#install.packages("stargazer")
#install.packages("car")
#install.packages("MASS")
#install.packages("caret")
#install.packages("stats")

library(stats)
library(caret)
library(MASS)
library(car)
library(stargazer)
library(regclass)
library(ggpubr)
library(gplots)
library(ggfortify)
library(multcompView)
library(tidyverse)
library(magrittr)   # piping related. %<>% is "<-" + "and then". both assigns and pipes.
library(officedown) # to change the text colors
library(officer)    # used with officedown
library(perm)
library(broom)
library(jmuOutlier) # source of perm test for median and trimmed means.
library(plyr)       # ddply
ft <- fp_text(color = 'mediumorchid4', bold = TRUE) # change the color of text easily
inline_hook <- function(x) {                # used in making the numbers print in decimal form instead of scientific notation
  if (is.numeric(x)) {
    format(x, digits = 9)
  } else x 
}
knitr::knit_hooks$set(inline = inline_hook) # this makes the numbers not print in scientific notation during inline code.
wrapper <- function(x,d=4) {
  round(x,d)
}
```

```{r read in dataset and set the mood, echo=F}
# Import the 2018 College Scorecard data and tidy it up.
CollegeSC18 <- read.csv("MERGED2018_19_PP.csv", stringsAsFactors = TRUE, na.strings = c("PrivacySuppressed","NULL","NaN","NA"))
CollegeSC18 <- tibble(CollegeSC18)
#CollegeSC18 %>% head(10)
personal_Palette <- c("#999999","#bae600", "#E6c500", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#CC79A7","mediumpurple","mediumpurple4",
                     "cornflowerblue","magenta3","royalblue4","orchid4","orchid3","orchid1","plum4","turquoise1","turquoise","turquoise4",
                     "violet","plum3","plum1","aquamarine","aquamarine3","aquamarine4","cyan","cyan4","cyan3")
cbPalette <- c("#999999", "#56B4E9", "#009E73", "#0072B2", "#CC79A7")
on_brand_Palette <- c("#ffc629","#b0b3b2","#9c5555","#7e6f9e","#52949a")

set.seed(59914120)
iters <- 10000

CollegeSC18 %<>% mutate("GRAD_CAT" = ifelse(is.na(OMAWDP8_ALL),NA,
                                            ifelse(OMAWDP8_ALL>.75,3,
                                                   ifelse(OMAWDP8_ALL>.50,2,
                                                          ifelse(OMAWDP8_ALL<.25,0,1)))))
CollegeSC18$GRAD_CAT <- as.factor(CollegeSC18$GRAD_CAT)
```

```{r}
CSC18_GRAD <- CollegeSC18 %>% filter(is.na(GRAD_CAT)==F) %>% filter(is.na(BBRR2_FED_UG_DFLT)==F)
Cat_var <- CSC18_GRAD$GRAD_CAT
Quant_var <- CSC18_GRAD$BBRR2_FED_UG_DFLT

Zero_data_GRAD <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="0") # <  30%
One_data_GRAD  <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="1") # >= 30%
Two_data_GRAD  <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="2") # >  65%
Three_data_GRAD  <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="3") # >  65%

G0 <- Zero_data_GRAD$BBRR2_FED_UG_DFLT
G1 <- One_data_GRAD$BBRR2_FED_UG_DFLT
G2 <- Two_data_GRAD$BBRR2_FED_UG_DFLT
G3 <- Three_data_GRAD$BBRR2_FED_UG_DFLT

med <- plyr::ddply(CSC18_GRAD, "GRAD_CAT", summarise, grp.median=median(BBRR2_FED_UG_DFLT))
```

```{r}
Ratio_of_MaxToMin_SD <- function(quant,categ){
  temp<-tapply(quant,categ,FUN=sd)
  ratio<-round(max(temp)/min(temp),2)
  #return(temp)
  print("The standard deviations of the quantitative variable for the different categorical levels are:")
  print(temp)
  print(paste("The ratio of the largest standard deviation to the smallest standard deviation is:", ratio))
}
```

## Executive Summary

1. Data Visualization and Description
2. K-Sample Permutation Tests
3. Parametric Anova
4. Kruskal-Wallis Test
5. Post-Hoc Test 
    a. Bonferroni
    b. Tukey's HSD
    c. LSD

|           This is where I will write my summary.












### Data Visualization and Description

|           This is where I will write about the visuals.

```{r Boxplot}
ggplot(CSC18_GRAD, aes(x=BBRR2_FED_UG_DFLT,fill=GRAD_CAT)) + 
       geom_histogram(binwidth=.034,color="black",closed="right") +
       scale_x_continuous(breaks=seq(0,1,.034)) + 
       scale_fill_manual(name="group",
                         values=on_brand_Palette[1:4],
                         labels=c("< 25%",">= 25% <= 50%","> 50 <= 75","> 75%")) +
       facet_grid(GRAD_CAT ~ .) + 
       xlab("Percentage of BBRR2_FED_UG_DFLT.(BBRR2_FED_UG_DFLT)") +
       labs(title= "Figure 1: Histogram of BBRR2_FED_UG_DFLT stratified by the categories of GRAD_CAT. (n = 5065)") +
       geom_vline(data=med, 
                  aes(xintercept=grp.median, color=GRAD_CAT),
                  linetype="dashed",
                  lwd=1.1,
                  show.legend = F) +
       stat_bin(aes(y=..count..,label=..count..),
                binwidth=.034, 
                geom="text",
                vjust=-.8) + theme_bw()

boxplot(Quant_var~Cat_var,
        names=c("< 25%",">= 25% <= 50%","> 50 <= 75","> 75%"), 
        main="Figure 2: Boxplot of BBRR2_FED_UG_DFLT stratified by the categories of GRAD_CAT. (n = 5065)", 
        boxwex=0.285, 
        xlab="GRAD_CAT", 
        ylab="BBRR2_FED_UG_DFLT",
        cex.lab=1.5,
        cex.main=1,
        cex.axis=1.5,
        col=on_brand_Palette[1:4]
        )

# Plot the mean point
points(2,mean(G1),pch=7)
points(1,mean(G0),pch=7)
points(3,mean(G2),pch=7)
points(4,mean(G3),pch=7)

# For the leftside boxplot
text(y = boxplot.stats(G0)$stats, 
     labels = paste(round(boxplot.stats(G0)$stats*100,2),"%",sep=""), 
     x = 1.305, 
     cex = 1.5)
text(y = round(max(G0),3), 
     labels = paste((round(max(G0),3)*100),"%",sep=""), 
     x =  1.35, 
     col = "black", 
     cex  =1.5)
text(y = round(mean(G0),3), 
     labels = paste((round(mean(G0),3)*100),"%",sep=""),
     x = 0.72,
     cex = 1.5)

# For the middleLeft boxplot
text(y = boxplot.stats(G1)$stats, 
     labels = paste(round(boxplot.stats(G1)$stats*100,2),"%",sep=""), 
     x = 2.3105, 
     col = "black",
     cex = 1.5)
text(y = round(mean(G1),3), # leftside 60%
     labels = paste((round(mean(G1),3)*100),"%",sep=""), 
     x = 1.72,
     col = "black",
     cex = 1.5)
text(y = round(max(G1),3), 
     labels = paste((round(max(G1),3)*100),"%",sep=""), 
     x =  2.36, 
     col = "black", 
     cex  =1.5)


# For the middleRight boxplot
text(y = boxplot.stats(G2)$stats, 
     labels = paste(round(boxplot.stats(G2)$stats*100,2),"%",sep=""), 
     x = 3.305, 
     col = "black",
     cex = 1.5)
text(y = round(mean(G2),3), # leftside 60%
     labels = paste((round(mean(G2),3)*100),"%",sep=""), 
     x = 2.745,
     col = "black",
     cex = 1.5)
text(y = round(max(G2),3), 
     labels = paste((round(max(G2),3)*100),"%",sep=""), 
     x =  3.35, 
     col = "black", 
     cex  =1.5)


# For the rightside boxplot
text(y = boxplot.stats(G3)$stats, 
     labels = paste(round(boxplot.stats(G3)$stats*100,2),"%",sep=""), 
     x = 4.305, 
     col = "black",
     cex = 1.5)
text(y = round(mean(G3),3), # leftside 60%
     labels = paste((round(mean(G3),3)*100),"%",sep=""), 
     x = 3.74,
     col = "black",
     cex = 1.5)
text(y = round(max(G3),3), 
     labels = paste((round(max(G3),3)*100),"%",sep=""), 
     x =  4.35, 
     col = "black", 
     cex  =1.5)


# QQ plot
qqnorm(G0,main="Figure 3.A: Q-Q plot for Default rate: G0",pch=19,cex.main=.83)
qqline(G0,col = "steelblue")
abline(v = 0, col="red")

# QQ plot
qqnorm(G1,main="Figure 3.B: Q-Q plot for Default rate: G1",pch=19,cex.main=.84)
qqline(G1,col = "steelblue")
abline(v = 0, col="red")

# QQ plot
qqnorm(G2,main="Figure 3.C: Q-Q plot for Default rate: G2",pch=19,cex.main=.84)
qqline(G2,col = "steelblue")
abline(v = 0, col="red")

# QQ plot
qqnorm(G3,main="Figure 3.D: Q-Q plot for Default rate: G3",pch=19,cex.main=.84)
qqline(G3,col = "steelblue")
abline(v = 0, col="red")
```

```{r Variance Check}
# Call Statement for the Function to check if the ratio of the largest standard deviation to the smalles standard deviation is less than 2, the rule of thumb for being able to pool.
Ratio_of_MaxToMin_SD(quant=Quant_var,categ=Cat_var) 

# Mean default rate for Graduation rates of 0% to 24%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="0"]),2),"%"))

# Mean default rate for Graduation rates of 25% to 49%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="1"]),2),"%"))

# Mean default rate for Graduation rates of 50% to 74%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="2"]),2),"%"))

# Mean default rate for Graduation rates of 75% to 100%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="3"]),2),"%"))

# Overall mean default rate
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT),2),"%"))
```

*******Since the variances are relatively equal but the data is very skewed, the appropriate analysis perm;permks() K-Sample Permutation F-Test 

### K-Sample Permutation Tests

|           This is where I will write about the k-sample permutation test.

```{r K-sample Permutation Test}
# Permutation-based p-value (using the Chi-Square Distribution approximation)
# pclt: using permutational central limit theorem
permKS(Quant_var~Cat_var,
       method='pclt')

# Exact Monte Carlo
permKS(Quant_var~Cat_var, 
       method='exact.mc',
       control=permControl(nmc=iters,seed=59914120))


```

```{r Tukey HSD}
model <- lm( Quant_var~Cat_var,CSC18_GRAD )
summary(model)
print("#####################################")
print("#####################################")
print("#####################################")
ANOVA <- aov(model)
ANOVA
print("#####################################")
print("#####################################")
print("#####################################")
tuk<-TukeyHSD(x=ANOVA, 'Cat_var', conf.level=0.95)
tuk
print("#####################################")
print("#####################################")
print("#####################################")
```

```{r Tukey Plot}
psig=as.numeric(apply(tuk$'Cat_var'[,2:3],1,prod)>=0)+1 # Psig controls the color of the confidence interval
op=par(mar=c(4.2,3,3.8,2)) # Second argument is the margin width on the left. The order is bottom, left, top, right

plot(tuk,col=psig,yaxt="n")

for (j in 1:length(psig)){
  axis(2,at=j,labels=rownames(tuk$'Cat_var')[length(psig)-j+1],
  las=1,                 
  cex.axis=.8,
  col.axis=psig[length(psig)-j+1])
}

par(op)
```

```{r Fisher's LSD}
library(agricolae)

temp<-anova(lm(Quant_var~Cat_var,data=CSC18_GRAD))  

mod2<-aov(Quant_var~Cat_var, data=CSC18_GRAD)

out<-LSD.test(mod2,
              "Cat_var",
              DFerror= temp$"Df"[2],
              MSerror= temp$"Mean Sq"[2],
              p.adj="none",
              alpha=.05,
              group=FALSE,
              console=TRUE)
out

plotmeans(Quant_var~Cat_var, 
          use.t=TRUE,
          digits=2, 
          bars=TRUE,
          barcol="blue",
          p=.95, 
          mean.labels=TRUE, 
          n.label=TRUE, 
          ci.label=TRUE,
          connect=TRUE,
          ccol="red",                       #COLOR OF LINES CONNECTING MEANS
          main="Plot of Sepal Length Means by Species of Iris",
          ylab="2-year Default rate",
          xlab="Graduation Category",
          legends=c("0","1","2","3"),
          cex.main=1.3, cex.lab=1.3, cex.axis=1.3)
```

```{r Bonferroni }
pairwise_ttest <- stats::pairwise.t.test(Quant_var,Cat_var,p.adj = "none")
pairwise_ttest_BONF <- stats::pairwise.t.test(Quant_var,Cat_var,p.adj = "bonferroni")
```



```{r}
Ratio_of_MaxToMin_SD(quant=Quant_var,categ=Cat_var)

ANOVA <- aov(Quant_var~Cat_var)

ANOVA_sum <- summary(ANOVA)

CSC18_GRAD %>%  select(BBRR2_FED_UG_DFLT) %>% summarize(mean = c(mean(G0),mean(G1),mean(G2),mean(G3)),
                                                        median = c(median(G0),median(G1),median(G2),median(G3)),
                                                             std = c(sd(G0),sd(G1),sd(G2),sd(G3)))





```

```{r}
pairwise_ttest
pairwise_ttest_BONF
```




























### Parametric Anova

|           This is where I will write about the parametric ANOVA.

```{r Parametric Anova}
summary(aov(Quant_var~Cat_var))
```

### Kruskal-Wallis Test

|           This is where I will write about the Kruskal-Wallis Test

```{r Kruskal-Wallis Test}
table(Cat_var)
kruskal.test(Quant_var~Cat_var, data = CSC18_GRAD)
```




### Post-Hoc Test 

|           This is where I will write about the Post-Hoc Tests

```{r Bonferroni}
#Compare the pvalues for the pairwise tests with no adjustment to the pvalues.  We can see that the Bonferroni adjustment leads to increased p-values to be more conservative.

pairwise.t.test(Quant_var,Cat_var, p.adj  = "none")

#Bonferroni adjustment

pairwise.t.test(Quant_var,Cat_var, p.adj  = "bonferroni")
```













```{r}

```











































































