---
title: "Deliverable Three"
author: "Nathaniel Jones"
output: word_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)
#install.packages("officedown")
#install.packages("officer")
#install.packages("magrittr")
#install.packages("tidyverse") 
#install.packages("ggpubr") 
#install.packages("gplots") 
#install.packages("multcompView") 

library(ggpubr)
library(gplots)
library(multcompView)
library(tidyverse)
library(magrittr)   # piping related. %<>% is "<-" + "and then". both assigns and pipes.
library(officedown) # to change the text colors
library(officer)    # used with officedown
library(perm)
library(jmuOutlier) # source of perm test for median and trimmed means.
library(plyr)       # ddply
ft <- fp_text(color = 'mediumorchid4', bold = TRUE) # change the color of text easily
inline_hook <- function(x) {                # used in making the numbers print in decimal form instead of scientific notation
  if (is.numeric(x)) {
    format(x, digits = 9)
  } else x 
}
knitr::knit_hooks$set(inline = inline_hook) # this makes the numbers not print in scientific notation during inline code.
wrapper <- function(x) {
  round(x,4)
}
```

```{r read in dataset and set the mood, echo=F}
# Import the 2018 College Scorecard data and tidy it up.
CollegeSC18 <- read.csv("MERGED2018_19_PP.csv", stringsAsFactors = TRUE, na.strings = c("PrivacySuppressed","NULL","NaN","NA"))
CollegeSC18 <- tibble(CollegeSC18)
#CollegeSC18 %>% head(10)
personal_Palette <- c("#999999","#bae600", "#E6c500", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#CC79A7","mediumpurple","mediumpurple4",
                     "cornflowerblue","magenta3","royalblue4","orchid4","orchid3","orchid1","plum4","turquoise1","turquoise","turquoise4",
                     "violet","plum3","plum1","aquamarine","aquamarine3","aquamarine4","cyan","cyan4","cyan3")
cbPalette <- c("#999999", "#56B4E9", "#009E73", "#0072B2", "#CC79A7")
```

```{r Subset and clean data,include=F}
# ALL
CollegeSC18 %>% select(BBRR2_FED_UG_DFLT,BBRR2_FED_UG_DLNQ,BBRR2_FED_UG_FBR,BBRR2_FED_UG_DFR,BBRR2_FED_UG_NOPROG,
                       BBRR2_FED_UG_MAKEPROG,BBRR2_FED_UG_PAIDINFULL,BBRR2_FED_UG_DISCHARGE) %>% summary()
# COMP
CollegeSC18 %>% select(BBRR2_FED_UGCOMP_DFLT,BBRR2_FED_UGCOMP_DLNQ,BBRR2_FED_UGCOMP_FBR,BBRR2_FED_UGCOMP_DFR,
                       BBRR2_FED_UGCOMP_NOPROG,BBRR2_FED_UGCOMP_MAKEPROG,BBRR2_FED_UGCOMP_PAIDINFULL,BBRR2_FED_UGCOMP_DISCHARGE) %>% summary()
# NOCOMP
CollegeSC18 %>% select(BBRR2_FED_UGNOCOMP_DFLT,BBRR2_FED_UGNOCOMP_DLNQ,BBRR2_FED_UGNOCOMP_FBR,BBRR2_FED_UGNOCOMP_DFR,
                       BBRR2_FED_UGNOCOMP_NOPROG,BBRR2_FED_UGNOCOMP_MAKEPROG,BBRR2_FED_UGNOCOMP_PAIDINFULL,BBRR2_FED_UGNOCOMP_DISCHARGE) %>% summary()
# UNK
CollegeSC18 %>% select(BBRR2_FED_UGUNK_DFLT,BBRR2_FED_UGUNK_DLNQ,BBRR2_FED_UGUNK_FBR,BBRR2_FED_UGUNK_DFR,BBRR2_FED_UGUNK_NOPROG,
                       BBRR2_FED_UGUNK_MAKEPROG,BBRR2_FED_UGUNK_PAIDINFULL,BBRR2_FED_UGUNK_DISCHARGE) %>% summary()

CSC18 <- CollegeSC18 %>% filter(PCTPELL > .5) %>% mutate("PROP_FLOAN_DefaultDeliquencyNOProgress_ALLUG" = BBRR2_FED_UG_DFLT + BBRR2_FED_UG_DLNQ + BBRR2_FED_UG_NOPROG)#,
                                                         #"PROP_FLOAN_")
  
#)

```

#### `r ftext('Executive Summary', ft)`

|       This is where you will make the claim.

- This is the most important result.
- The next most important result.
- The next most important result.

* Table goes here *
*                 *
*                 *
*                 *

I. table of contents   
II. this will be filled later   
III. after things are created   
IV. adskfja;sdkfj;   

#### `r ftext('Visuals and Descriptive Statistics', ft)`

```{r Visuals and Descriptive Statistics }

```

:: ALL ::   
BBRR2_FED_UG_DFLT,BBRR2_FED_UG_DLNQ,BBRR2_FED_UG_FBR,BBRR2_FED_UG_DFR,BBRR2_FED_UG_NOPROG,BBRR2_FED_UG_MAKEPROG,BBRR2_FED_UG_PAIDINFULL,BBRR2_FED_UG_DISCHARGE   
:: COMP ::   
BBRR2_FED_UGCOMP_DFLT,BBRR2_FED_UGCOMP_DLNQ,BBRR2_FED_UGCOMP_FBR,BBRR2_FED_UGCOMP_DFR,BBRR2_FED_UGCOMP_NOPROG,BBRR2_FED_UGCOMP_MAKEPROG,BBRR2_FED_UGCOMP_PAIDINFULL,BBRR2_FED_UGCOMP_DISCHARGE   
:: NOCOMP ::   
BBRR2_FED_UGNOCOMP_DFLT,BBRR2_FED_UGNOCOMP_DLNQ,BBRR2_FED_UGNOCOMP_FBR,BBRR2_FED_UGNOCOMP_DFR,BBRR2_FED_UGNOCOMP_NOPROG,BBRR2_FED_UGNOCOMP_MAKEPROG,BBRR2_FED_UGNOCOMP_PAIDINFULL,BBRR2_FED_UGNOCOMP_DISCHARGE   
:: UNK ::   
BBRR2_FED_UGUNK_DFLT,BBRR2_FED_UGUNK_DLNQ,BBRR2_FED_UGUNK_FBR,BBRR2_FED_UGUNK_DFR,BBRR2_FED_UGUNK_NOPROG,BBRR2_FED_UGUNK_MAKEPROG,BBRR2_FED_UGUNK_PAIDINFULL,BBRR2_FED_UGUNK_DISCHARGE   

#### `r ftext('Conclusions from the Parametric ANOVA F-test', ft)`

```{r Parametric ANOVA F-test}

```

#### `r ftext('Conclusions from the K-Sample Permutation F-Tests', ft)`

```{r K-Sample Permutation F-Tests}

```

#### `r ftext('Conclusions from the Kruskal-Wallis Test', ft)`

```{r Kruskal-Wallis Test}

```

#### `r ftext('Post-hoc test: Bonferroni', ft)`

```{r}

```

#### `r ftext('Post-hoc test: Tukey Honestly Significant Difference(HSD)', ft)`

```{r}

```

#### `r ftext('Post-hoc test: Fisher Least Significant Difference(LSD)', ft)`

```{r}

```






























