---
title: "Deliverable Two"
author: "Nathaniel Jones"
date: "4/2/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)
#install.packages("officedown")
#install.packages("officer")
#install.packages("magrittr")
#install.packages("tidyverse") 

library(tidyverse)
library(magrittr)   # piping related. %<>% is "<-" + "and then". both assigns and pipes.
library(officedown) # to change the text colors
library(officer)    # used with officedown
library(perm)
library(jmuOutlier) # source of perm test for median and trimmed means.
library(plyr)       # ddply
ft <- fp_text(color = 'mediumorchid4', bold = TRUE) # change the color of text easily
inline_hook <- function(x) {                # used in making the numbers print in decimal form instead of scientific notation
  if (is.numeric(x)) {
    format(x, digits = 9)
  } else x 
}
knitr::knit_hooks$set(inline = inline_hook) # this makes the numbers not print in scientific notation during inline code.
```

```{r read in dataset and set the mood, echo=FALSE}
# Import the 2018 College Scorecard data and tidy it up.
CollegeSC18 <- read.csv("MERGED2018_19_PP.csv", stringsAsFactors = TRUE, na.strings = c("PrivacySuppressed","NULL","NaN","NA"))
CollegeSC18 <- tibble(CollegeSC18)
#CollegeSC18 %>% head(10)
personal_Palette <- c("#999999","#bae600", "#E6c500", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#CC79A7","mediumpurple","mediumpurple4",
                     "cornflowerblue","magenta3","royalblue4","orchid4","orchid3","orchid1","plum4","turquoise1","turquoise","turquoise4",
                     "violet","plum3","plum1","aquamarine","aquamarine3","aquamarine4","cyan","cyan4","cyan3")
cbPalette <- c("#999999", "#56B4E9", "#009E73", "#0072B2", "#CC79A7")
```

```{r Creation of the Binary variables}
CSC18 <- CollegeSC18 %>% filter(MAIN == 1) %>% select(INSTNM,PCTPELL,FTFTPCTPELL,PREDDEG,HIGHDEG,CONTROL,LOCALE,ICLEVEL,OPENADMP,OPEFLAG,HCM2)
CSC18 %<>% mutate("PCTPELL_CAT" = ifelse(is.na(PCTPELL)!=T,               # Check if missing. IF not True, THEN continue, ELSE go to **
                                         ifelse(PCTPELL <= .5,0,          # Check Condition One, return 0 if true, 
                                                1),                       # ELSE return 1
                                         NA),                             # ** Return NA
                  "FTFTPCTPELL_CAT" = ifelse(is.na(FTFTPCTPELL)!=T,       # Check if missing. IF not True, THEN continue, ELSE go to **
                                             ifelse(FTFTPCTPELL <= .5,0,  # Check Condition One, return 0 IF true,
                                                    1),                   # ELSE return 1
                                             NA),                         # ** Return NA
                  "PREDDEG_CAT" = ifelse(is.na(PREDDEG)!=T,               # Check if missing. IF not True, THEN continue, ELSE go to **
                                         ifelse(PREDDEG == 0,NA,          # Check Condition One, return NA if true,
                                                ifelse(PREDDEG == 3,1,    # Check Condition Two, return 1 if true
                                                       0)),               # ELSE return 0
                                         NA),                             # ** Return NA
                  "HIGHDEG_CAT" = ifelse(is.na(HIGHDEG)!=T,               # Check if missing. IF not True, THEN continue, ELSE go to **
                                         ifelse(HIGHDEG == 0,NA,          # Check Condition One, return NA if true,
                                                ifelse(HIGHDEG == 3,1,    # Check Condition Two, return 1 if true,
                                                       0)),               # ELSE return 0
                                         NA),                             # ** Return NA
                  "CONTROL_CAT" = ifelse(is.na(CONTROL)!=T,               # Check if missing. IF not True, THEN continue, ELSE go to **
                                         ifelse(CONTROL == 1,0,           # Check Condition One, return 0 if true,
                                                1),                       # Else return 1
                                         NA),                             # ** Return NA
                  "ICLEVEL_CAT" = ifelse(is.na(ICLEVEL)!=T,               # Check if missing. IF not True, THEN continue, ELSE go to **
                                         ifelse(ICLEVEL == 1,0,           # Check Condition One, return 0 if true,
                                                1),                       # ELSE return 1
                                         NA),                             # ** Return NA
                  "LOCALE_CAT" = ifelse(is.na(LOCALE) != T,               # Check if missing. IF not True, THEN continue, ELSE go to **
                                        ifelse(LOCALE >= 33,1,            # Check Condition One, return 1 if true,
                                               0),                        # ELSE return 0
                                        NA),                              # ** Return NA
                  "OPEFLAG_CAT" = ifelse(is.na(OPEFLAG)!=T,               # Check if missing. IF not True, THEN continue, ELSE go to **
                                         ifelse(OPEFLAG == 1,0,           # Check Condition One, return 0 if true,
                                                ifelse(OPEFLAG == 2,0,    # Check Condition Two, return 0 if true,
                                                       1)),               # ELSE return 1
                                         NA))                             # ** Return NA
CSC18

#CSC18 %>% select(PCTPELL,PCTPELL_CAT,FTFTPCTPELL,FTFTPCTPELL_CAT) %>% summary()                              # No filter summary
#CSC18 %>% select(PCTPELL,PCTPELL_CAT,FTFTPCTPELL,FTFTPCTPELL_CAT) %>% filter(PCTPELL_CAT == 1) %>% summary() # Greater than or equal to 50% Pell Recipient
#CSC18 %>% select(PCTPELL,PCTPELL_CAT,FTFTPCTPELL,FTFTPCTPELL_CAT) %>% filter(PCTPELL_CAT != 1) %>% summary() # Less than 50% Pell Recipient
#CSC18 %>% select(PCTPELL,PCTPELL_CAT,FTFTPCTPELL,FTFTPCTPELL_CAT) %>% filter(FTFTPCTPELL_CAT == 1) %>% summary() # Greater than or equal to 50% Pell Recipient
#CSC18 %>% select(PCTPELL,PCTPELL_CAT,FTFTPCTPELL,FTFTPCTPELL_CAT) %>% filter(FTFTPCTPELL_CAT != 1) %>% summary() # Less than 50% Pell Recipient
#CSC18 %>% select(PREDDEG,PREDDEG_CAT,HIGHDEG,HIGHDEG_CAT) %>% filter(PREDDEG == 3) %>% summary() # summary of predominantly bachelor degree granting
#CSC18 %>% select(PREDDEG,PREDDEG_CAT,HIGHDEG,HIGHDEG_CAT) %>% filter(HIGHDEG == 3) %>% summary() # summary of highest degree awarded == bachelor
#CSC18 %>% select(CONTROL,CONTROL_CAT) %>% filter(CONTROL == 1) %>% summary() # IF CONTROL == 1, THEN CONTROL_CAT == 0.(PUBLIC(0) UNI- else PRIVATE(1) UNI-)
#CSC18 %>% select(ICLEVEL,ICLEVEL_CAT) %>% filter(ICLEVEL == 1) %>% summary() # IF ICLEVEL == 1, THEN ICLEVEL_CAT == 0.(4-YR(0) UNI- else <4-YR(1) UNI-)
#CSC18 %>% select(LOCALE,LOCALE_CAT) %>% filter(LOCALE > 32) %>% summary()    # IF LOCALE > 33, THEN LOCALE_CAT == 1.  (URBAN LOCALE(0) UNI- else RURAL LOCALE(1) UNI-)
#CSC18 %>% select(OPEFLAG,OPEFLAG_CAT) %>% filter(OPEFLAG > 2) %>% summary() # IF OPEFLAG > 2, THEN OPEFLAG_CAT == 1. (NO Title IV PARTICIPATION RESTRICTION(0) else T4 RESTRICTION(1))

# Change type to factor since they are binary and not numeric


CSC18$HCM2 <- as.factor(CSC18$HCM2)
CSC18$PCTPELL_CAT <- as.factor(CSC18$PCTPELL_CAT)
CSC18$FTFTPCTPELL_CAT <- as.factor(CSC18$FTFTPCTPELL_CAT)
CSC18$PREDDEG_CAT <- as.factor(CSC18$PREDDEG_CAT)
CSC18$HIGHDEG_CAT <- as.factor(CSC18$HIGHDEG_CAT)
CSC18$CONTROL_CAT <- as.factor(CSC18$CONTROL_CAT)
CSC18$ICLEVEL_CAT <- as.factor(CSC18$ICLEVEL_CAT)
CSC18$LOCALE_CAT <- as.factor(CSC18$LOCALE_CAT)
CSC18$OPEFLAG_CAT <- as.factor(CSC18$OPEFLAG_CAT)
CSC18$OPENADMP <- as.factor(CSC18$OPENADMP)

CSC18 %<>% select(-PREDDEG,-HIGHDEG,-CONTROL,-LOCALE,-ICLEVEL,-OPEFLAG)
```

```{r Handle Missing values}
CSC18 # 5345 obs
working_CSC18 <- CSC18 %>% filter(is.na(PCTPELL)!=T)
#working_CSC18 %>% summary()
working_CSC18 # 5065 obs

working_CSC181 <- working_CSC18 %>% filter(is.na(FTFTPCTPELL)!=T)
working_CSC181 %>% summary()
working_CSC181 # 4864 obs

working_CSC182 <- working_CSC18 %>% filter(is.na(OPENADMP)!=T)
#working_CSC182 %>% summary()
working_CSC182 # 4954 obs

working_CSC183 <- working_CSC18 %>% filter(is.na(HIGHDEG_CAT)!=T)
#working_CSC183 %>% summary()
working_CSC183 # 5057 obs
```

```{r FTFTPCTPELL_CAT}
mu <- plyr::ddply(working_CSC181, "FTFTPCTPELL_CAT", summarise, grp.mean=mean(PCTPELL))

h1 <- ggplot(working_CSC181, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(FTFTPCTPELL_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by FTFTPCTPELL_CAT")
```

```{r OPENADMP}
mu <- plyr::ddply(working_CSC182, "OPENADMP", summarise, grp.mean=mean(PCTPELL))

h2 <- ggplot(working_CSC182, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(OPENADMP ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by OPENADMP")
```

```{r HCM2}
mu <- plyr::ddply(working_CSC181, "HCM2", summarise, grp.mean=mean(PCTPELL))

h3 <- ggplot(working_CSC181, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(HCM2 ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by HCM2")
```

```{r PREDDEG_CAT}
mu <- plyr::ddply(working_CSC181, "PREDDEG_CAT", summarise, grp.mean=mean(PCTPELL))

h4 <- ggplot(working_CSC181, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(PREDDEG_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by PREDDEG_CAT")
```

```{r HIGHDEG_CAT}
mu <- plyr::ddply(working_CSC183, "HIGHDEG_CAT", summarise, grp.mean=mean(PCTPELL))

h5 <- ggplot(working_CSC183, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(HIGHDEG_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by HIGHDEG_CAT")
```

```{r CONTROL_CAT}
mu <- plyr::ddply(working_CSC181, "CONTROL_CAT", summarise, grp.mean=mean(PCTPELL))

h6 <- ggplot(working_CSC181, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(CONTROL_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by CONTROL_CAT")
```

```{r ICLEVEL_CAT}
mu <- plyr::ddply(working_CSC181, "ICLEVEL_CAT", summarise, grp.mean=mean(PCTPELL))

h7 <- ggplot(working_CSC181, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(ICLEVEL_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by ICLEVEL_CAT")
```

```{r LOCALE_CAT}
mu <- plyr::ddply(working_CSC181, "LOCALE_CAT", summarise, grp.mean=mean(PCTPELL))

h8 <- ggplot(working_CSC181, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(LOCALE_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by LOCALE_CAT")
```

```{r OPEFLAG_CAT}
mu <- plyr::ddply(working_CSC181, "OPEFLAG_CAT", summarise, grp.mean=mean(PCTPELL))

h9 <- ggplot(working_CSC181, aes(x=PCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(OPEFLAG_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of undergraduate students who received a pell grant stratified by OPEFLAG_CAT")
working_CSC181 %>% filter(OPEFLAG_CAT == 1 & PCTPELL_CAT == 0)
working_CSC181 %>% filter(OPEFLAG_CAT == 1 & PCTPELL_CAT == 1)
CollegeSC18 %>% filter(INSTNM == "Fashion Focus Hair Academy") %>% select(INSTNM,CONTROL,PREDDEG,HIGHDEG)
```

```{r PCTPELL as the QUANTITATIVE VARIABLE}
h1
h2
h3
h4
h5
h6
h7
h8
h9
```
```{r Handle Missing values2}
CSC18 # 5345 obs
working_CSC18 <- CSC18 %>% filter(is.na(FTFTPCTPELL)!=T)
#working_CSC18 %>% summary()
working_CSC18 # 5065 obs

working_CSC181 <- working_CSC18 %>% filter(is.na(PCTPELL)!=T)
working_CSC181 %>% summary()
working_CSC181 # 4864 obs

working_CSC182 <- working_CSC18 %>% filter(is.na(OPENADMP)!=T)
#working_CSC182 %>% summary()
working_CSC182 # 4954 obs

working_CSC183 <- working_CSC18 %>% filter(is.na(HIGHDEG_CAT)!=T)
#working_CSC183 %>% summary()
working_CSC183 # 5057 obs
```

```{r PCTPELL_CAT}
mu <- plyr::ddply(working_CSC181, "PCTPELL_CAT", summarise, grp.mean=mean(FTFTPCTPELL))

h1 <- ggplot(working_CSC181, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(PCTPELL_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by PCTPELL_CAT")
```

```{r OPENADMP}
mu <- plyr::ddply(working_CSC182, "OPENADMP", summarise, grp.mean=mean(FTFTPCTPELL))

h2 <- ggplot(working_CSC182, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(OPENADMP ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by OPENADMP")
```

```{r HCM2}
mu <- plyr::ddply(working_CSC181, "HCM2", summarise, grp.mean=mean(FTFTPCTPELL))

h3 <- ggplot(working_CSC181, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(HCM2 ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by HCM2")
```

```{r PREDDEG_CAT}
mu <- plyr::ddply(working_CSC181, "PREDDEG_CAT", summarise, grp.mean=mean(FTFTPCTPELL))

h4 <- ggplot(working_CSC181, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(PREDDEG_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by PREDDEG_CAT")
```

```{r HIGHDEG_CAT}
mu <- plyr::ddply(working_CSC183, "HIGHDEG_CAT", summarise, grp.mean=mean(FTFTPCTPELL))

h5 <- ggplot(working_CSC183, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(HIGHDEG_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by HIGHDEG_CAT")
```

```{r CONTROL_CAT}
mu <- plyr::ddply(working_CSC181, "CONTROL_CAT", summarise, grp.mean=mean(FTFTPCTPELL))

h6 <- ggplot(working_CSC181, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(CONTROL_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by CONTROL_CAT")
```

```{r ICLEVEL_CAT}
mu <- plyr::ddply(working_CSC181, "ICLEVEL_CAT", summarise, grp.mean=mean(FTFTPCTPELL))

h7 <- ggplot(working_CSC181, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(ICLEVEL_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by ICLEVEL_CAT")
```

```{r LOCALE_CAT}
mu <- plyr::ddply(working_CSC181, "LOCALE_CAT", summarise, grp.mean=mean(FTFTPCTPELL))

h8 <- ggplot(working_CSC181, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(LOCALE_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by LOCALE_CAT")
```

```{r OPEFLAG_CAT}
mu <- plyr::ddply(working_CSC181, "OPEFLAG_CAT", summarise, grp.mean=mean(FTFTPCTPELL))

h9 <- ggplot(working_CSC181, aes(x=FTFTPCTPELL)) +
       geom_histogram(color="black", fill=sample(personal_Palette,1)) +
       facet_grid(OPEFLAG_CAT ~ .) +
       geom_vline(data=mu, aes(xintercept=grp.mean, color="red"),
                  linetype="dashed") +
       labs(title= "Histogram of the percent of First-time Full-time undergraduate students who received a pell grant stratified by OPEFLAG_CAT")
```

```{r FTFTPCTPELL as the QUANTITATIVE VARIABLE}
h1
h2
h3
h4
h5
h6
h7
h8
h9
```

```{r}
Zero_data <- subset(CSC18, subset = CSC18$PREDDEG_CAT=="0")
One_data  <- subset(CSC18, subset = CSC18$PREDDEG_CAT=="1")

ggplot() + 
  stat_qq(aes(sample = Zero_data$PCTPELL), colour = "green") + 
  stat_qq(aes(sample = One_data$PCTPELL), colour = "red") +
  geom_abline(aes(slope = Zero_data$PCTPELL, intercept = .95), linetype = 2)
```























































#### `r ftext('Background Information and Variable description', ft)`

|       asdf





#### `r ftext('Hypothesis and Results', ft)`

```{r}

```



#### `r ftext('Subset, Histogram, and Boxplot', ft)`

```{r Subsets}

```


```{r Histogram}
plant_labels<-factor(widge$Plant,levels=c("D","N"), labels=c("Dallas","Norcross"))
#plant_labels
colorsBW_single <- c("gray90")  # once the colorsBW variable is defined you do not have to keep running it.
colorsBW_many <- c("gray90", "gray70", "gray50", "gray80", "gray60")
histogram(~widge$PRDCTY|plant_labels,
          main="Figure 8: Histogram of Productivity by Plant (n=40)",
          xlab="Productivity Scores (0 to 100 points)",
          type="percent",
          breaks=seq(from=60, to=100, by=5),
          layout=c(1,2),   # 1 column and 2 rows
          col=colorsBW_single
          ) 
```

```{r Boxplot}
ggplot(df, aes(varx,vary)) +
       stat_boxplot(geom ='errorbar') +
       geom_boxplot(aes(fill = sample(personal_Palette,2)),width=.6,
                    position = position_dodge(preserve = "single")) +
       ggtitle("Frequency of Weathersit by Season") + 
       xlab("Season") + ylab("Frequency") +
       scale_fill_manual(values = colors) +
       labs(fill = "Weathersit")
```


#### `r ftext('Check for normality', ft)`

```{r}
# QQ plot
qqnorm(vari,main="Figure 3: Q-Q plot for the Average Net Price (n = 2284)",pch=19)
qqline(vari,col = "steelblue")
abline(v = 0, col="red")
abline(h = c(order_vari[1095], order_vari[1190],18500),
       col = c("sandybrown","sandybrown","red"),
       lty = c(1,1,2),
       lwd = c(1,1,3))

shap_wilk <- shapiro.test(vari)
#shap_wilk
#shap_wilk$p.value
```



#### `r ftext('Conclusions from the Parametric t-test on the difference of two population centers', ft)`

```{r}

stats::t.test(var1,var2,
              alternative= "two.sided",
              mu=0, paired = F, 
              var.equal=F,
              conf.level=.95)


```



#### `r ftext('Conclusions from the Permutation test on the difference of two population means', ft)`

```{r}
perm::permTS(var1,var2,                          # no sig diff in centers
             method="exact.mc",                  # 
             control=permControl(nmc=100,        # 
                                 seed=59914120)) # ALWAYS set seed

```



#### `r ftext('Conclusions from the Permutation test on the difference of two population medians', ft)`

```{r}
jmuOutlier::perm.test(var1,var2, 
          stat=median,
          alternative="two.sided",
          mu=0,
          paired=FALSE,
          plot=FALSE,
          all.perms=TRUE, # does exact unless computing the exac p-value takes more than num.sim calculations
          num.sim=20000) # default number of permutations, runs instantaneously, 100000 takes about 30 secs.

```



#### `r ftext('Conclusion from Permutation test on the difference of two population trimmed means', ft)`

```{r}
jmuOutlier::perm.test(var1,var2,
                      stat=mean, trim=0.10,     # trim by 10%
                      alternative="two.sided",
                      all.perms=TRUE, mu=0, 
                      paired=FALSE, plot=FALSE,
                      num.sim=10000)


```



#### `r ftext('Conclusion from the Wilcoxon Rank Sum test on the difference of two population centers', ft)`

```{r}
stats::wilcox.test(var1,var2,)

```


#### `r ftext('Conclusion from the RMD (Ratio Mean Difference) test', ft)`

```{r}
RMD.test(var1,var2,
         nsamp=100) 
```




#### `r ftext('Conclusion from the Kolmogorov-Smirnov test on the difference of shape, center, and spread.', ft)`

```{r}
stats::ks.test(var1,var2,)
```



