---
title: "Deliverable 3"
author: "Nathaniel Jones"
output: word_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=12, fig.height=8)
# install.packages("officedown")
# install.packages("officer")
# install.packages("magrittr")
# install.packages("tidyverse") 
# install.packages("ggpubr") 
# install.packages("gplots") 
# install.packages("ggfortify")
# install.packages("broom") 
# install.packages("multcompView") 
# install.packages('regclass')
# install.packages("stargazer")
# install.packages("car")
# install.packages("MASS")
# install.packages("caret")
# install.packages("stats")

library(stats)
library(caret)
library(MASS)
library(car)
library(stargazer)
library(regclass)
library(ggpubr)
library(gplots)
library(ggfortify)
library(multcompView)
library(tidyverse)
library(magrittr)   # piping related. %<>% is "<-" + "and then". both assigns and pipes.
library(officedown) # to change the text colors
library(officer)    # used with officedown
library(perm)
library(broom)
library(jmuOutlier) # source of perm test for median and trimmed means.
library(plyr)       # ddply
library(agricolae)
ft <- fp_text(color = 'mediumorchid4', bold = TRUE) # change the color of text easily
inline_hook <- function(x) {                # used in making the numbers print in decimal form instead of scientific notation
  if (is.numeric(x)) {
    format(x, digits = 9)
  } else x 
}
knitr::knit_hooks$set(inline = inline_hook) # this makes the numbers not print in scientific notation during inline code.
wrapper <- function(x,d=4) {
  round(x,d)
}
```

```{r read in dataset and set the mood, echo=F}
# Import the 2018 College Scorecard data and tidy it up.
CollegeSC18 <- read.csv("Para_Nonpara_Directed_Study/2Deliverable_Three/COMPLETE/MERGED2018_19_PP.csv", stringsAsFactors = TRUE, na.strings = c("PrivacySuppressed","NULL","NaN","NA"))
CollegeSC18 <- tibble(CollegeSC18)
#CollegeSC18 %>% head(10)
personal_Palette <- c("#999999","#bae600", "#E6c500", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#CC79A7","mediumpurple","mediumpurple4",
                     "cornflowerblue","magenta3","royalblue4","orchid4","orchid3","orchid1","plum4","turquoise1","turquoise","turquoise4",
                     "violet","plum3","plum1","aquamarine","aquamarine3","aquamarine4","cyan","cyan4","cyan3")
cbPalette <- c("#999999", "#56B4E9", "#009E73", "#0072B2", "#CC79A7")
on_brand_Palette <- c("#ffc629","#b0b3b2","#9c5555","#7e6f9e","#52949a")

set.seed(59914120)
iters <- 10000

CollegeSC18 %<>% mutate("GRAD_CAT" = ifelse(is.na(OMAWDP8_ALL),NA,
                                            ifelse(OMAWDP8_ALL>.75,"Q4",
                                                   ifelse(OMAWDP8_ALL>.50,"Q3",
                                                          ifelse(OMAWDP8_ALL<.25,"Q1","Q2")))))
CollegeSC18$GRAD_CAT <- as.factor(CollegeSC18$GRAD_CAT)
```

```{r Data manipulation and subsetting, echo=F,include=T}
CSC18_GRAD <- CollegeSC18 %>% filter(is.na(GRAD_CAT)==F) %>% filter(is.na(BBRR2_FED_UG_DFLT)==F) #%>% select(INSTNM)
Cat_var <- CSC18_GRAD$GRAD_CAT
Quant_var <- CSC18_GRAD$BBRR2_FED_UG_DFLT

Zero_data_GRAD <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="Q1")   # [0%, 25%)    : 0.00 <= to <  0.25
One_data_GRAD  <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="Q2")   # [25%, 50%]   : 0.25 <= to <= 0.50
Two_data_GRAD  <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="Q3")   # (50%, 75%]   : 0.50 <  to <= 0.75
Three_data_GRAD  <- subset(CSC18_GRAD, subset = CSC18_GRAD$GRAD_CAT=="Q4") # (75%, 100%]  : 0.75 <  to <= 100

G0 <- Zero_data_GRAD$BBRR2_FED_UG_DFLT
G1 <- One_data_GRAD$BBRR2_FED_UG_DFLT
G2 <- Two_data_GRAD$BBRR2_FED_UG_DFLT
G3 <- Three_data_GRAD$BBRR2_FED_UG_DFLT

med <- plyr::ddply(CSC18_GRAD, "GRAD_CAT", summarise, grp.median=median(BBRR2_FED_UG_DFLT))
```

```{r Functions, echo=F,include=F}
# Equality of Variance function
Ratio_of_MaxToMin_SD <- function(quant,categ,prnt=1){
  temp<-tapply(quant,categ,FUN=sd)
  ratio<-round(max(temp)/min(temp),2)
  if(prnt==1){
      print("The standard deviations of the quantitative variable for the different categorical levels are:")
      print(temp)
      print(paste("The ratio of the largest standard deviation to the smallest standard deviation is:", ratio))
  } else {return(temp)}
}

#


```

# `r ftext('Table of Contents', ft)`

EXECUTIVE SUMMARY (Pg. 1-3)  
-  **Hypothesis**    
-  **Summary of Findings**    
-  **Actionable Items**    

# `r ftext('Appendix', ft)`

A.  DATA MANIPULATION (Pg. 4)
B.  ARE THE VARIANCES EQUAL? (Pg. 4)
C.  DO THE K-LEVELS FOLLOW A NORMAL DISTRIBUTION? (Pg. 5-7)
D.  NONPARAMETRIC TEST: K-Sample Permutation (Pg. 8)
E.  POST-HOC PROCEDURES (Pg. 8-9)

# `r ftext('EXECUTIVE SUMMARY', ft)`

**Hypothesis:** Is there a relationship between loan default rate and graduation rate quartiles?"

**Summary of Findings:**

For post-secondary institutions, the "average" default rate for students who default within 2-years was calculated for the four-year graduation rate quartiles: 

- less than or equal to 25% (Q1), 
- greater than 25% to 50% (Q2), 
- greater than 50% to 75% (Q3), and 
- over 75% (Q4). 

The nonparametric K-sample permutation test was used to detect difference between the graduation rate quartiles for the reason that the data displayed evidence of skewness and did not display evidence suggesting that it was normally distributed. There is a significant difference in the default rates for all four quartiles except the third and fourth quartiles. 

\newpage

**Actionable items:**

-  The median 2-year default rate for undergraduates from institutions with higher graduation rates (Q3 and Q4) is about 5% for both quartiles. 
-  In comparison, the median default rates for institutions with low graduation rates (Q1 and Q2) were 13% and 11%, respectively.
-  Thus, institutions who graduate more than 50% of their students tend to have significantly lower loan default rates. 
-  However, the default rate does not decrease for institutions that graduate more than 75% of their undergraduates.
-  Notably, we see that the institutions in Q3 and Q4 are more skewed to the left side of the plot than institutions in Q1 and Q2.

```{r Histogram, echo=F,include=T}
ggplot(CSC18_GRAD, aes(x=BBRR2_FED_UG_DFLT,fill=GRAD_CAT)) + 
       geom_histogram(binwidth=.034,color="black",closed="right") +
       scale_x_continuous(breaks=seq(0,1,.034)) +
       scale_fill_manual(name="Graduation rate quartiles",
                         values=on_brand_Palette[1:4],
                         labels=c("Q1: [0%, 25%)","Q2: [25%, 50%]","Q3: (50%, 75%]","Q4: (75%, 100%]")) +
       facet_grid(GRAD_CAT ~ .) + 
       xlab("Percent of undergraduates defaulting on their federal loans within 2 years of exiting the university. (BBRR2_FED_UG_DFLT)") +
       ylab("Frequency of universities at a given default rate") + 
       labs(title= "Figure 1: Histogram for the 2-year Student Default Rate by each Graduation Rate Quartile.") +
       geom_vline(data=med, 
                  aes(xintercept=grp.median, color=GRAD_CAT),
                  linetype="dashed",
                  lwd=1.1,
                  show.legend = F) +
       stat_bin(aes(y=..count..,label=..count..),
                binwidth=.034, 
                geom="text",
                vjust=-.8) + theme_bw()
```

\newpage

-  Although Q3 and Q4 have similar medians, the default loan rates are more variable for the institutions with graduation rates greater than 75% (Q4).
-  In fact, Q4 institutions had a standard deviation of loan default rates of 5.87% while Q3 had a standard deviation of 4.34%.
-  This suggests that institutions that achieve the highest possible graduation rate may not inherently yield the lowest possible 2-year loan default rate.

```{r Boxplot, echo=F,include=T}
boxplot(Quant_var~Cat_var,
        names=c("Q1: [0%, 25%)","Q2: [25%, 50%]","Q3: (50%, 75%]","Q4: (75%, 100%]"), 
        main="Figure 2: Boxplot for the 2-year Student Default Rate by each Graduation Rate Quartile.", 
        boxwex=0.285, 
        xlab="Graduation rate quartiles", 
        ylab="Percent of undergraduates defaulting on their federal loans within 2 years of exiting the university. ",
        cex.lab=.95,
        cex.main=1,
        cex.axis=1.5,
        col=on_brand_Palette[1:4]
        )

# Plot the mean point
points(2,mean(G1),pch=7)
points(1,mean(G0),pch=7)
points(3,mean(G2),pch=7)
points(4,mean(G3),pch=7)

# For the leftside boxplot
text(y = boxplot.stats(G0)$stats, 
     labels = paste(round(boxplot.stats(G0)$stats*100,2),"%",sep=""), 
     x = 1.305, 
     cex = 1.5)
text(y = round(max(G0),3), 
     labels = paste((round(max(G0),3)*100),"%",sep=""), 
     x =  1.35, 
     col = "black", 
     cex  =1.5)
text(y = round(mean(G0),3), 
     labels = paste((round(mean(G0),3)*100),"%",sep=""),
     x = 0.72,
     cex = 1.5)

# For the middleLeft boxplot
text(y = boxplot.stats(G1)$stats, 
     labels = paste(round(boxplot.stats(G1)$stats*100,2),"%",sep=""), 
     x = 2.3105, 
     col = "black",
     cex = 1.5)
text(y = round(mean(G1),3), # leftside 60%
     labels = paste((round(mean(G1),3)*100),"%",sep=""), 
     x = 1.72,
     col = "black",
     cex = 1.5)
text(y = round(max(G1),3), 
     labels = paste((round(max(G1),3)*100),"%",sep=""), 
     x =  2.36, 
     col = "black", 
     cex  =1.5)


# For the middleRight boxplot
text(y = boxplot.stats(G2)$stats, 
     labels = paste(round(boxplot.stats(G2)$stats*100,2),"%",sep=""), 
     x = 3.305, 
     col = "black",
     cex = 1.5)
text(y = round(mean(G2),3), # leftside 60%
     labels = paste((round(mean(G2),3)*100),"%",sep=""), 
     x = 2.745,
     col = "black",
     cex = 1.5)
text(y = round(max(G2),3), 
     labels = paste((round(max(G2),3)*100),"%",sep=""), 
     x =  3.35, 
     col = "black", 
     cex  =1.5)


# For the rightside boxplot
text(y = boxplot.stats(G3)$stats, 
     labels = paste(round(boxplot.stats(G3)$stats*100,2),"%",sep=""), 
     x = 4.305, 
     col = "black",
     cex = 1.5)
text(y = round(mean(G3),3), # leftside 60%
     labels = paste((round(mean(G3),3)*100),"%",sep=""), 
     x = 3.74,
     col = "black",
     cex = 1.5)
text(y = round(max(G3),3), 
     labels = paste((round(max(G3),3)*100),"%",sep=""), 
     x =  4.35, 
     col = "black", 
     cex  =1.5)
```

\newpage

# `r ftext('APPENDIX', ft)`

### `r ftext('A. DATA MANIPULATION', ft)`

There were 2,789 observations analyzed in this report. The variables used are defined as:

+-------------------+----------------------------------------------------------------------------------+
| Variable label    | Definition                                                                       |
+===================+==================================================================================+
| BBRR2_FED_UG_DFLT | The percent of undergraduates that default on their federal loan within 2-years. |
+-------------------+----------------------------------------------------------------------------------+
| OMAWDP8_ALL       | The percent of undergraduates that graduated within 8-years.                     |
+-------------------+----------------------------------------------------------------------------------+

A categorical variable was created by splitting the percent of undergraduate students that graduate from a post-secondary institution within 8 years into four equal-sized bins. These bins ranged from 0% to 25%, greater than 25% to 50%, greater than 50% to 75%, and greater than 75%. They were then given the labels Quartile 1 (Q1), Quartile 2 (Q2), Quartile 3 (Q3), and Quartile 4 (Q4), respectively.

#####    

+---------------+----------------+-----------------+----------------+-----------------+
|               | Quartile 1     | Quartile 2      | Quartile 3     | Quartile 4      |
+===============+================+=================+================+=================+
| Percent range | 0% <= x <= 25% | 25% < x <= 50%  | 50% < x <= 75% | 75% < x <= 100% |
+---------------+----------------+-----------------+----------------+-----------------+

#####  

## `r ftext('B. ARE THE VARIANCES EQUAL?', ft)`

The variance among the four quartiles is approximately equal. Table 1 displays the standard deviation for each of the 4 quartiles. The largest standard deviation (Q4, 0.5872) is only 1.42 times larger than the smallest standard deviation (Q1, 0.4136).

Since the cutoff point for considering the variance to be approximately equal is 2, our data has NOT violated the assumption of equal variance.

```{r Check for equal variance, echo=F,include=F}
# Call Statement for the Function to check if the ratio of the largest standard deviation to the smalles standard deviation is less than 2, the rule of thumb for being able to pool.
tab <- Ratio_of_MaxToMin_SD(quant=Quant_var,categ=Cat_var,prnt=0) 

CSC18_GRAD %<>% filter(!is.na(BBRR2_FED_UG_DFLT))


# Mean default rate for Graduation rates of 0% to 24%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="Q1"]),2),"%"))

# Mean default rate for Graduation rates of 25% to 49%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="Q2"]),2),"%"))

# Mean default rate for Graduation rates of 50% to 74%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="Q3"]),2),"%"))

# Mean default rate for Graduation rates of 75% to 100%
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT[CSC18_GRAD$GRAD_CAT=="Q4"]),2),"%"))

# Overall mean default rate
print(paste(round(100*mean(CSC18_GRAD$BBRR2_FED_UG_DFLT),2),"%"))
```

\newpage

+---------------+----------------+-----------------+----------------+-----------------+
|               | Quartile 1     | Quartile 2      | Quartile 3     | Quartile 4      |
+===============+================+=================+================+=================+
| Percent range | 0% <= x <= 25% | 25% < x <= 50%  | 50% < x <= 75% | 75% < x <= 100% |
+---------------+----------------+-----------------+----------------+-----------------+
| Default Rate  | 0.04136        | 0.04557         | 0.04341        | 0.05872         |
+---------------+----------------+-----------------+----------------+-----------------+

: Table 1: Standard Deviations

#####  

## `r ftext('C. DO THE K-LEVELS FOLLOW A NORMAL DISTRIBUTION?', ft)`

The four quartiles display evidence of skewness. Figures 4, 5, 6, and 7 display Q-Q plots for the four graduation rate quartiles. Each of these plots display values on the left and right side to be above what we would expect (indicated by the blue line) if the data was normally distributed, indicating a significant deviation from normality. Since the interquartile variance is approximately equal and the data did not display evidence suggesting that it was normally distributed, the nonparametric K-sample permutation test will be used over the parametric ANOVA test and the Kruskal-Wallis test.

Notably, on the left side of each of the plots we see that the sample is above the blue line suggesting that there was more institutions with loan default rates closer to 0% than what we would expect if the data is normally distributed. For Q1 in Figure 4, we can see that the left side of the plot mostly follows what would be expected if the data was normally distributed but with a slight deviation above the blue line. In comparison, Q2 in Figure 5, we can see on the left side of the plot that the deviation above the blue line is much greater than the deviation seen for Q1. Similarly, we can see in Figure 6 (for Q3) and 7 (for Q4) that the data further deviates from the blue line. This information suggests that institutions with higher graduation rates will have more institutions with loan default rates close to zero.

```{r Q-Q plot, echo=F,include=T}
# QQ plot
qqnorm(G0,main="Figure 4: Q-Q plot for Default rate: Q1",pch=19,cex.main=.83,col=on_brand_Palette[1])
qqline(G0,col = "steelblue")
abline(v = 0, col="black")

# QQ plot
qqnorm(G1,main="Figure 5: Q-Q plot for Default rate: Q2",pch=19,cex.main=.84,col=on_brand_Palette[2])
qqline(G1,col = "steelblue")
abline(v = 0, col="black")

# QQ plot
qqnorm(G2,main="Figure 6: Q-Q plot for Default rate: Q3",pch=19,cex.main=.84,col=on_brand_Palette[3])
qqline(G2,col = "steelblue")
abline(v = 0, col="black")

# QQ plot
qqnorm(G3,main="Figure 7: Q-Q plot for Default rate: Q4",pch=19,cex.main=.84,col=on_brand_Palette[4])
qqline(G3,col = "steelblue")
abline(v = 0, col="black")
```

\newpage

#####  

## `r ftext('D. NONPARAMETRIC TEST: K-Sample Permutation', ft)`

The results of this test showed that there is a difference in the default rate between each of the quartiles. In fact, I am 99% confident that the true p-value is between 0 and 0.0005. This indicates that at least one of the distributions has a shift in location that is significantly different from the other quartiles. Further analysis will be conducted via Tukey's HSD, Fisher's LSD, and Bonferroni's correction in the next section.

```{r, echo=F,include=T}
# Permutation-based p-value (using the Chi-Square Distribution approximation)
# pclt: using permutational central limit theorem
permKS(Quant_var~Cat_var,
       method='pclt')

# Exact Monte Carlo
permKS(Quant_var~Cat_var, 
       method='exact.mc',
       control=permControl(nmc=iters,seed=59914120))
```

## `r ftext('E. POST-HOC PROCEDURES', ft)`

Three post-hoc procedures were performed: Tukey's HSD, Fisher's LSD, and Bonferroni's correction. These procedures are used to investigate which quartiles contained differences and which did not. From the output of the Tukey's HSD test, we see that Quartiles 2 and 3 did not significantly differ from each other. Quartiles 0 and 1 did display a difference with each other as well as with Quartile 3. Thus, I am 95% confident that the true difference in the centers for Quartile 2 and 2 is between -0.047 and -0.037. The results of the Tukey's HSD test can be visualized by the figure below. Fisher's LSD and Bonferroni's correction did not disagree with the Tukey's HSD test. These tests found no difference between Quartile 3 and 3 but did find a difference between Quartiles 0, 1, and 2.

```{r Tukey HSD, echo=F,results='asis'}
model <- lm( Quant_var~Cat_var, CSC18_GRAD )
#summary(model)
#print("#####################################")
#print("#####################################")
#print("#####################################")
ANOVA <- aov(model)
#ANOVA
#print("#####################################")
#print("#####################################")
#print("#####################################")
tuk <- TukeyHSD(x=ANOVA, 'Cat_var', conf.level=0.95)
tuk$Cat_var %>% knitr::kable(caption="Table *: Tukey HSD",digits=4)
#print("#####################################")
#print("#####################################")
#print("#####################################")

```

```{r Tukey Plot, echo=F,include=T}
psig <- as.numeric(apply(tuk$'Cat_var'[,2:3],1,prod)>=0)+1 # Psig controls the color of the confidence interval
op <- par(mar=c(4.2,3,3.8,2)) # Second argument is the margin width on the left. The order is bottom, left, top, right

plot(tuk,col=psig,yaxt="n")  # ,main="Figure 8: Tukey HSD plot of 95% family-wise confidence level",xlab="Difference in the mean levels of institutional default rates"

for (j in 1:length(psig)){
  axis(2,at=j,labels=rownames(tuk$'Cat_var')[length(psig)-j+1],
  las=1,                 
  cex.axis=.8,
  col.axis=psig[length(psig)-j+1])
}

par(op)
```

```{r Fishers LSD, echo=F,include=F}
temp<-anova(lm(Quant_var~Cat_var,data=CSC18_GRAD))  

mod2<-aov(Quant_var~Cat_var, data=CSC18_GRAD)

out<-LSD.test(mod2,
              "Cat_var",
              DFerror= temp$"Df"[2],
              MSerror= temp$"Mean Sq"[2],
              p.adj="none",
              alpha=.05,
              group=FALSE,
              console=TRUE)
```

```{r Fishers LSD tables, echo=F,results='asis'}
out$statistics %>% knitr::kable(caption="Table *: Fishers LSD statistics",digits=4)
out$means %>% knitr::kable(caption="Table *: Fishers LSD means by Quartile",digits=4)
out$comparison %>% knitr::kable(caption="Table *: Fishers LSD interquartile comparison",digits=4)
```

```{r LSD output, echo=F,include=T}
plotmeans(Quant_var~Cat_var, 
          use.t=TRUE,
          digits=2, 
          bars=TRUE,
          barcol="blue",
          p=.95, 
          mean.labels=TRUE, 
          n.label=TRUE, 
          ci.label=TRUE,
          connect=TRUE,
          ccol="red",                       #COLOR OF LINES CONNECTING MEANS
          main="Figure 9: Plot of the mean default rates by Graduation Category",
          ylab="2-year undergraduate Default rate",
          xlab="Graduation Quartile",
          legends=c("Q1","Q2","Q3","Q4"),
          cex.main=1.3, cex.lab=1.3, cex.axis=1.3)
```

```{r Bonferroni correction, echo=F,results='asis'}
pairwise_ttest <- stats::pairwise.t.test(Quant_var,Cat_var,p.adj = "none")
pairwise_ttest$p.value %>% knitr::kable(caption="Table *: Pairwise t-test")
pairwise_ttest_BONF <- stats::pairwise.t.test(Quant_var,Cat_var,p.adj = "bonferroni")
pairwise_ttest_BONF$p.value %>% knitr::kable(caption="Table *: Pairwise t-test with Bonferroni correction")
```

## `r ftext('Other unused tests', ft)`

The Kruskal-Wallis test was not used since the variance of this sample was found to be approximately equal. The K-sample permutation test was chosen to be used over the ANOVA because each of the quartiles exhibited heavy skewness.

```{r Parametric Anova,echo=F,include=F}
summary(aov(Quant_var ~ Cat_var))
```

```{r Kruskal Wallis,echo=F,include=F}
table(Cat_var)
kruskal.test(Quant_var ~ Cat_var, data = CSC18_GRAD)
```
